Trait plasticity and covariance along a continuous soil moisture gradient

### 2021-09-06 FVT Manuscript/manuscript.tex
revisions

  \title{Trait plasticity and covariance along a continuous soil moisture gradient}
    \author{J. Grey Monroe\textsuperscript{1}, Haoran Cai\textsuperscript{2}, \& David L. Des Marais\textsuperscript{2,3}}
    \date{}

\shorttitle{Function-valued drought extremes}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Department of Plant Sciences, University of California at Davis, Davis, USA\\\textsuperscript{2} Department of Civil and Environmental Engineering, Massachusetts Institute of Technology, Cambridge, MA, USA\\\textsuperscript{3} The Arnold Arboretum of Harvard University. Boston, MA, USA}
\keywords{drought, function-valued traits, Brachypodium, evolutionary constraint, phenotypic plasticity, non-linearity}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

Correspondence concerning this article should be addressed to J. Grey Monroe, 262 Robbins Hall, UC Davis, One Shields Ave, Davis CA 95616. E-mail: \href{mailto:greymonroe@gmail.com}{\nolinkurl{greymonroe@gmail.com}}}

@@

We thank Chase Mason and Eric Goolsby for insightful conversations about function-valued trait approaches. This work was supported by an Eco-Evo-Devo Network training grant to JGM.

@@

\begin{figure*}[!h]
\includegraphics[width=\textwidth]{../Figures/maps} \caption{Distributions of (a) \emph{B. distachyon} and (b) \emph{B. sylvaticum} reported on GBIF as of 2019.18.08. Examples of (c) \emph{B. distachyon} Carly Slawson (CC BY 4.0, \url{https://www.inaturalist.org/photos/42532397}) and (d) \emph{B. sylvaticum} Grzegorz Grzejszczak (CC BY-NC 4.0, \url{https://www.inaturalist.org/photos/3608899}).}\label{fig:maps}
\end{figure*}

>>>>

  \title{Trait plasticity and covariance along a continuous soil moisture gradient}
    \author{J. Grey Monroe\textsuperscript{1,4}, Haoran Cai\textsuperscript{2}, \& David L. Des Marais\textsuperscript{2,3}}
    \date{}

\shorttitle{Function-valued drought extremes}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Department of Plant Sciences, University of California at Davis, Davis, USA\\\textsuperscript{2} Department of Civil and Environmental Engineering, Massachusetts Institute of Technology, Cambridge, MA, USA\\\textsuperscript{3} The Arnold Arboretum of Harvard University. Boston, MA, USA\\\textsuperscript{4} Max Planck Institute for Developmental Biology, Tubingen, DE}
\keywords{drought, function-valued traits, Brachypodium, evolutionary constraint, phenotypic plasticity, non-linearity}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

Correspondence concerning this article should be addressed to J. Grey Monroe, Current address: 1 Max Planck Ring, 72076 Tubingen, DE. E-mail: \href{mailto:greymonroe@gmail.com}{\nolinkurl{greymonroe@gmail.com}}}

@@

We thank Chase Mason and Eric Goolsby for insightful conversations about function-valued trait approaches. This work was supported by an Eco-Evo-Devo Network training grant, USDA-NIFA Award 2014-38420-21801, and Max Planck Society support for JGM.

@@

\begin{figure*}[!h]
\includegraphics[width=\textwidth]{../Figures/maps} \caption{Distributions of (a) \emph{B. distachyon} and (b) \emph{B. sylvaticum} reported on GBIF as of 2019.18.08. Examples of (c) \emph{B. distachyon} Carly Slawson (CC BY 4.0, \url{https://www.inaturalist.org/photos/42532397}) and (d) \emph{B. sylvaticum} Grzegorz Grzejszczak (CC BY-NC 4.0, \url{https://www.inaturalist.org/photos/36088991}) (GBIF.org (26 February 2020) GBIF Occurrence Download \url{https://doi.org/10.15468/dl.rau5v9}).}\label{fig:maps}
\end{figure*}
